Predicted cardiovascular risk for US adults with diabetes, chronic kidney disease, and \u2265 65 years of age overall and with stage 1 hypertension

### 2021-03-23 doc/ACCAHA_BP_groups.Rmd
seminar update

---
title: "Predicted cardiovascular risk for US adults with diabetes, chronic kidney disease, and \u2265 65 years of age overall and with stage 1 hypertension"
bibliography: refs.bib
csl: ccqo.csl
output: 
  officedown::rdocx_document:
    reference_docx: style_manuscript_times_new_roman_lines.docx
---

@@

# misc functions for the paper

>>>>

---
title: "Predicted cardiovascular risk for US adults with diabetes, chronic kidney disease, and \u2265 65 years of age overall and with stage 1 hypertension"
bibliography: refs.bib
csl: ccqo.csl
always_allow_html: true
output: 
  officedown::rdocx_document:
    reference_docx: style_manuscript_times_new_roman_lines.docx
---

@@
